---
title: "Application Risk Scoring"
author: "NIKHIL AIVALLI"
date: "February 10, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Read data
```{r warning=FALSE}
CR <- read.csv('D:/IMARTICUS/SAS Class/Application Risk Scoring/Application Risk Scoring(Nikhil)/trainset.csv')
#View(CR)
#attach(CR)

```
#EDA
#EDA:Remove irrelevant variables
```{r warning=FALSE}
CR$Credit=as.factor(CR$Credit)
class(CR$Credit)
CR$Random=NULL
#Identify missing values using colSums 
summary(CR)
sum(is.na(CR))
colSums(is.na(CR))
```
#Classification using decision tree
```{r warning=FALSE}
library(rpart)
model_CR_DL = rpart(Credit~.,data=CR) # classification
```
#classification using Logistic Regression
```{r warning=FALSE}
model_CR_LR<- glm(Credit~balance_credit_acc+duration+moral+sparkont+beszeit+rate+famges+buerge+verm+alter+weitkred,family = binomial(link = 'logit'),data=CR)
summary(model_CR_LR)
```
#classification using SVM
```{r warning=FALSE}
library(e1071)
model_CR_SVM<- svm(formula=Credit~.,data=CR,type='C-classification',kernel='linear')
summary(model_CR_SVM)
```
#classification using NAIVE BAYES
```{r warning=FALSE}
library(e1071)
model_CR_NB<-naiveBayes(Credit~.,data=CR)
```

#classification using random forest
```{r warning=FALSE}
library(randomForest)
model_CR_RF<-randomForest(x=CR[,-1],
                      y=CR[,1],
                      ntree = 20)
#summary(model_CR_RF)

```
```{r}
#detach(CR)
```
#VALIDATION DATASET 
```{r warning=FALSE}
CR_V<- read.csv('D:/IMARTICUS/SAS Class/Application Risk Scoring/Application Risk Scoring(Nikhil)/validateset.csv')
CR_V$Random=NULL
CR_V$Credit=as.factor(CR_V$Credit)
#View(CR_V)
#attach(CR_V)
acc<-function(cf1){
  Totp<-cf1[1,1]+cf1[1,2]+cf1[2,1]+cf1[2,2]
  TP<-cf1[1,1]+cf1[2,2]
  c<-TP/Totp
  c
}
```
#Classification & validation using KNN
```{r warning=FALSE}
library(class)
model_CR_KNN=knn(train =CR[,-1] ,
              test = CR_V[,-1],
              cl=CR[,1],
              k=20,prob = TRUE)
model_CR_KNN<-as.numeric(model_CR_KNN)

CF_CR_KNN<- table(model_CR_KNN,CR_V$Credit)
CF_CR_KNN


acc(CF_CR_KNN)   # 0.7222222  72.22%
library(ROCR)

pr_CR_KNN<- prediction(model_CR_KNN,CR_V$Credit)
#length(cr_v$Loan_Status)
prf_CR_KNN<- performance(pr_CR_KNN,measure = "tpr",x.measure = "fpr")
plot(prf_CR_KNN)

#obtaining area under ROC curve
auc_CR_KNN<-performance(pr_CR_KNN,measure = "auc")
auc_CR_KNN<- auc_CR_KNN@y.values[[1]]
auc_CR_KNN
```

#validating using decision tree
```{r warning=FALSE}
#CR_V$Credit=as.numeric(CR_V$Credit)
validate_CR_DL <- predict(model_CR_DL,newdata=CR_V,type = 'class')
#validate_CR_DL <- ifelse(validate_CR_DL>=0.5,1,0)
validate_CR_DL<-as.numeric(validate_CR_DL)

#Confusion matrix
cf_CR_DL<-table(validate_CR_DL,CR_V$Credit)
cf_CR_DL
#function for accuracy

acc(cf_CR_DL)   #0.7326389 73.26%

library(ROCR)


pr_CR_DL<- prediction(validate_CR_DL,CR_V$Credit)
#length(cr_v$Loan_Status)
prf_CR_DL<- performance(pr_CR_DL,measure = "tpr",x.measure = "fpr")
plot(prf_CR_DL)

#obtaining area under ROC curve
auc_CR_DL<-performance(pr_CR_DL,measure = "auc")
auc_CR_DL<- auc_CR_DL@y.values[[1]]
auc_CR_DL

#prediction for the prediction set
plot(model_CR_DL,uniform=TRUE,cex=0.8)
text(model_CR_DL, use.n=TRUE, all=TRUE)

```









#validating using logistic regression
```{r warning=FALSE}
#validation of our model using validation set
validate_CR_LR <- predict(model_CR_LR,newdata=CR_V,type='response')
validate_CR_LR <- ifelse(validate_CR_LR >=0.5,1,0)

#Confusion matrix
cf_CR_LR<-table(validate_CR_LR,CR_V$Credit)
cf_CR_LR
#function for accuracy

acc(cf_CR_LR)   #0.7638889 76.38%

library(ROCR)

pr_CR_LR<- prediction(validate_CR_LR,CR_V$Credit)
#length(cr_v$Loan_Status)
prf_CR_LR<- performance(pr_CR_LR,measure = "tpr",x.measure = "fpr")
plot(prf_CR_LR)

#obtaining area under ROC curve
auc_CR_LR<-performance(pr_CR_LR,measure = "auc")
auc_CR_LR<- auc_CR_LR@y.values[[1]]
auc_CR_LR
#help(ROCR)
```
#validating using SVM
```{r warning=FALSE}
#predicting 
validate_CR_SVM<-predict(model_CR_SVM,CR_V)

validate_CR_SVM=as.numeric(validate_CR_SVM)
#validate_CR_SVM<-ifelse(validate_CR_SVM=="Y",1,0)
#confusion matrix
cf_CR_SVM<-table(validate_CR_SVM,CR_V$Credit)
cf_CR_SVM

#function for accuracy

acc(cf_CR_SVM)

library(ROCR)
pr_CR_SVM<- prediction(validate_CR_SVM,CR_V$Credit)
#length(cr_v$Loan_Status)
prf_CR_SVM<- performance(pr_CR_SVM,measure = "tpr",x.measure = "fpr")
plot(prf_CR_SVM)

#obtaining area under ROC curve
auc_CR_SVM<-performance(pr_CR_SVM,measure = "auc")
auc_CR_SVM<- auc_CR_SVM@y.values[[1]]
auc_CR_SVM
#help(ROCR)

```
#validating using NAIVE BAYES
```{r warning=FALSE}
#predicting 
validate_CR_NB<-predict(model_CR_NB,CR_V)
validate_CR_NB<-as.numeric(validate_CR_NB)
#validate_CR_NB<-ifelse(validate_CR_NB=="Y",1,0)
#confusion matrix
cf_CR_NB<-table(validate_CR_NB,CR_V$Credit)
cf_CR_NB

#function for accuracy

acc(cf_CR_NB) #0.7048611   70.48%

library(ROCR)
pr_CR_NB<- prediction(validate_CR_NB,CR_V$Credit)
prf_CR_NB<- performance(pr_CR_NB,measure = "tpr",x.measure = "fpr")
plot(prf_CR_NB)

#obtaining area under ROC curve
auc_CR_NB<-performance(pr_CR_NB,measure = "auc")
auc_CR_NB<- auc_CR_NB@y.values[[1]]
auc_CR_NB
```
#validating using RANDOM FOREST
```{r warning=FALSE}
validate_CR_RF<- predict(model_CR_RF,newdata =CR_V)
validate_CR_RF<-as.numeric(validate_CR_RF)
#validate_CR_RF <- ifelse(validate_CR_RF >=0.5,1,0)

CF_RF<-table(validate_CR_RF,CR_V$Credit)
CF_RF

acc(CF_RF)  #0.7777778  77.77%

library(ROCR)

pr_CR_RF<- prediction(validate_CR_RF,CR_V$Credit)
#length(cr_v$Loan_Status)
prf_CR_RF<- performance(pr_CR_RF,measure = "tpr",x.measure = "fpr")
plot(prf_CR_RF)

#obtaining area under ROC curve
auc_CR_RF<-performance(pr_CR_RF,measure = "auc")
auc_CR_RF<- auc_CR_RF@y.values[[1]]
auc_CR_RF
```
#From above models ,it is observed that Logistic Regression HAS HIGHEST ACCURECY 
```{r warning=FALSE}
CR_V=data.frame(CR_V,validate_CR_LR)
View(CR_V)
write.csv(CR_V,file = "validate(accurecy,report).csv")
```